### 2022-05-26 chapters/04-chapter-4.tex
txs auto checkin

Tabel \ref{testcase} akan menjelaskan kasus-kasus pengujian sistem PRA.
\begin{small}
	\begin{longtable}{ | p{1cm} | p{3.5cm} | p{4cm} | p{4cm} | }
			\caption{Daftar \textit{service} dan fungsi yang akan dimodifikasi}
			\label{testcase}                                                           
			\\ \hline
			\centering\bfseries{No} & \centering\bfseries{Nama Service} & \centering\bfseries{Nama Fungsi} & \centering\bfseries{Metode } \tabularnewline \hline
			\endfirsthead
	%		1 & AdService &  cookware \\ \hline
			1 & CheckoutService &  placeorder  \\ \hline
			2 & CurrencyService &  convert \\ \hline
			3 & EmailService &  sendorderconfirmation \\ \hline
			4 & PaymentService &  charge \\ \hline
			5 & ProductCatalogService &  getproduct \\ \hline
			6 & RecommendationService &  listrecommendations \\ \hline
			7 & ShippingService &  getquote \\ \hline		
		\end{longtable}
\end{small}

>>>>

Tabel \ref{testcase} akan menjelaskan kasus-kasus pengujian sistem PRA.
\begin{small}
	\begin{adjustwidth}{-2cm}{}
		\begin{longtable}{ | p{1cm} | p{3.5cm} | p{3.5cm} | p{3.5cm} | }
			\caption{Daftar \textit{service} dan fungsi yang akan dimodifikasi}
			\label{testcase}                                                           
			\\ \hline
			\centering\bfseries{No} & \centering\bfseries{Nama Service} & \centering\bfseries{Nama Fungsi} & \centering\bfseries{Metode} \tabularnewline \hline
			\endfirsthead
			1 & AdService &  cookware & hoo \\ \hline

		\end{longtable}
	\end{adjustwidth}
\end{small}
